Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2022-08-24 tex/sections/intro.tex
Mention the ASAR
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

At the time of writing of this document,
the total mining reward for a Bitcoin block is around \$150,000. If we assume, in decision theoretic terminology,
that the mining reward accurately defines the utility function of a Bitcoin miner, one could hire all hashing power
of the Bitcoin network for one hour by
spending only \$750,000. The situation is not much different for PoS blockchains, as long as the total
stake of the validator set is a relatively small value. By
stake, we mean a real number measuring the total interest of a user in the system, and we are not referring, in
particular, to some locked amount of a user's money that is known as stake in some PoS protocols.
This problem is more severe in blockchains that use randomly selected small sets of validators. These small sets
usually have low total stake and could be easily bribed and corrupted. Selecting these random sets
by hidden random procedures would not help, since the validator himself knows he has been selected, before casting
his vote.

@@

Securing a computer system against cyberattacks needs planning ahead and access to engineering resources.
Special software and hardware, like custom-built operating systems and isolated specialized hardware are required.
This is not something a normal user can afford. But powerful centralized entities, having large financial and
technical resources, could actually build
systems that are resilient against sophisticated cyberattacks. In this regard, we have to admit, a centralized system is
arguably superior to a decentralized\footnote{Note that decentralized and distributed are two different concepts.}
system.

@@

More formally, each CI statement has the form $\tau_{\mathbb{S}, \hat{\mathbb{S}}, \mathbb{R}}$, and states that
$\hat{\mathbb{S}}$ is the commitment of the next state after executing an ordered list of external requests with
commitment $\mathbb{R}$ on a state which has commitment $\mathbb{S}$.
Commitments to states are produced by a cryptographic accumulator.
Validators can\footnote{Using the Argennon cloud is optional for a validator.} receive succinct cryptographic proofs
of these CI statements (STARK/SNARK) from the Argennon cloud and validate blocks without storing the ledger state
or performing costly computation.

@@

Argennon applications (i.e smart contracts) are stored in a high level text based language on the blockchain. This
language is intended for preserving the
high level information of the application logic to facilitate platform specific compiler optimization at a host
machine. This enables delegates to compile and optimize Argennon applications for their specific hardware platforms
and execute applications efficiently, ensuring the state transition can be found as fast as possible. Moreover,
validators by using a special compiler, generate arithmetization of this language and use it for verifying CI proofs.

@@

Using Succinct Argument of Knowledge systems makes the main functionalities of an Argennon validator light enough to
be implemented as a smart contract. By deploying a validator contract on another platform, Argennon
could use more established blockchains as an extra layer of security, specially
during the bootstrapping phase, when ARG is not well distributed yet. In addition, this contract will facilitate
trustless bridging of assets from that platform to the Argennon blockchain. To reduce the execution fee, only
roll-ups of the state transition can be validated by the contract.

>>>>

At the time of writing of this document,
the total mining reward for a Bitcoin block is around \$150,000. If we assume, in decision theoretic terminology,
that the mining reward accurately defines the utility function of a Bitcoin miner, one could hire all hashing power
of the Bitcoin network for one hour by
spending only \$750,000. The situation is not much different for PoS blockchains, as long as the total
stake of the validator set is a relatively small value. By
stake, we mean a real number measuring the total interest of a user in the system, we are not referring, in
particular, to some locked amount of a user's money that is known as stake in some PoS protocols.
This problem is more severe in blockchains that use randomly selected small sets of validators. These small sets
usually have low total stake and could be easily bribed and corrupted. Selecting these random sets
by hidden random procedures would not help, since the validator himself knows he has been selected, before casting
his vote.

@@

Securing a computer system against cyberattacks needs planning ahead and access to engineering resources.
Special software and hardware, like custom-built operating systems and isolated specialized hardware are required.
This is not something a normal user can afford. Powerful centralized entities, having large financial and
technical resources, could build
systems that are resilient against sophisticated cyberattacks. In this regard, we have to admit, a centralized system is
arguably superior to a decentralized\footnote{Note that decentralized and distributed are two different concepts.}
system.

@@

More formally, each CI statement has the form
$\hat{\mathbb{S}} \coloneqq \tau(\mathbb{S}, \mathbb{R})$, and states that
$\hat{\mathbb{S}}$ is the commitment of the next state after executing an ordered list of external requests with
commitment $\mathbb{R}$ on a state which has commitment $\mathbb{S}$.
Commitments to states are produced by a cryptographic accumulator. $\tau$ is a transition function and is known to
both the validator and the prover.

Validators can\footnote{Using the Argennon cloud is optional for a validator.} receive succinct cryptographic proofs
(STARK/SNARK) of these CI statements from the Argennon cloud and validate blocks without storing the ledger
state or performing costly computation.

@@

On the blockchain, Argennon applications (i.e smart contracts) are stored in a high level text based language, called
the Argennon Standard Application Representation (ASAR). The ASAR is intended for preserving the
high level information of the application logic to facilitate platform specific compiler optimization at a host
machine. This enables delegates to compile and optimize Argennon applications for their specific hardware platforms
and execute applications efficiently, ensuring the state transition can be found as fast as possible. Moreover,
validators by using a special compiler, generate arithmetization of this language and use it for verifying CI proofs.

@@

Using Succinct Argument of Knowledge systems makes the main functionalities of an Argennon validator light enough to
be implemented as a smart contract. By deploying a validator contract on another platform, Argennon
could use more established blockchains as an extra layer of security, specially
during the bootstrapping phase, when ARG is not well distributed yet. In addition, this contract will facilitate
trustless bridging of assets from that platform to the Argennon blockchain. To reduce execution fee, only
roll-ups of the state transition can be validated by the contract.
